---
title: 'Course Project: Shiny Application and Reproducible Pitch'
author: "Anup Kumar Mishra"
date: "30 October 2018"
output:
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Diamond Analysis Report

Diamond Data Analysis Report enabled developing data products using shiny apps being embeded within RMarkDown.

Using PageUp and PageDown keys all the slides can be traversed.

## Application Overview

- Diamonds Properties can be analysed using several Parameters.
- Carat,Price,sample size,color Depth are some of the common parameters.
- This Report enables to pick the right parameters for the best Diamond selection.


## Slide with Complete Reporting Appliaction

Click the Below Link for the Application.

https://anupkumar08.shinyapps.io/myApp/

Click the link below for compiled project files on gitub repo.

https://github.com/aanupkumar08/Peer-graded-Assignment-Course-Project-Shiny-Application-and-Reproducible-Pitch

## Data Used
The data used for this application is diamonds data set, which is part of ggplot2 package. Containing information about 53940 diamonds with 10 variables.

```{r, echo=TRUE}
library("ggplot2")
head(diamonds)
```

Plot

Here we can see the relationship between three variables: miles per gallon (mpg), displacement (disp) and weight (wt).

```{r}
library(car)
scatterplotMatrix(~mpg+disp+wt, data=mtcars, cex.axis=1.5)
```